Attention Towards Distance Education Tools During COVID-19 Pandemic: Evidence from Google Trends

### 2021-12-26 Paper_online_Learning.tex
edit typo

The term distance education is known by a variety of names. The terms such as distance learning, e-Learning, online learning environments, home study, independent study, external
study, correspondence education, off campus study, open learning and open education are used commonly and interchangeably \autocite{moore2011learning}. It often describes the effort of providing access to learning for those who are geographically distant. The definition also stated that distance education uses emerging media and associated experiences to produce distributed learning opportunities. Few common features found in all these terms is they all involve some form of instruction occurs between two parties; learners and teachers, different times, places and/or varying forms of instructional materials \autocite{moore2011learning}. There are different types of interactions that facilitate learners to construct knowledge in distance education environments. These are learner--content interactions, learner--instructor interactions, learner--learner interactions and learner--interface interaction \autocite{wallace2003online}.

>>>>

The term distance education is known by a variety of names such as distance learning, e-Learning, online learning, home study, independent study, external study, correspondence education, off campus study, open learning and open education \autocite{moore2011learning}. Few common features found in all these terms are, they all involve some form knowledge sharing between two parties; learners and educators, different times, different geographical locations and/or varying forms of instructional materials and tools \autocite{moore2011learning}. Further, there are different types of interactions such are learner--content interactions, learner--instructor interactions, learner--learner interactions and learner--interface interaction that can facilitate learners to construct knowledge in distance education environments. These \autocite{wallace2003online}.

### 2021-12-26 main.Rmd
edit typo

The term distance education is known by a variety of names. The terms such as distance learning, e-Learning,  online learning environments, home study, independent study, external
study, correspondence education, off campus study, open learning and open education  are used commonly and interchangeably  [@moore2011learning]. It often describes the effort of providing access to learning for those who are geographically distant. The definition also stated that distance education uses emerging media and associated experiences to produce distributed learning opportunities. Few common features found in all these terms is they all involve some form of instruction occurs between two parties; learners and teachers, different times, places  and/or  varying forms of instructional materials [@moore2011learning]. There are different types  of interactions that facilitate learners to construct knowledge in distance education environments. These are learner–content interactions, learner–instructor interactions, learner–learner interactions and  learner–interface interaction [@wallace2003online].

>>>>

The term distance education is known by a variety of names such as distance learning, e-Learning,  online learning, home study, independent study, external study, correspondence education, off campus study, open learning and open education [@moore2011learning]. Few common features found in all these terms are, they all involve some form knowledge sharing between two parties; learners and educators, different times, different geographical locations  and/or  varying forms of instructional materials and tools [@moore2011learning]. Further, there are different types  of interactions such are learner–content interactions, learner–instructor interactions, learner–learner interactions and  learner–interface interaction that can facilitate learners to construct knowledge in distance education environments. These [@wallace2003online].
